### 2019-05-06 2-Chapters/3-Chapter/chapter3.tex
Lots of new plots.

We consider the nine following algorithms. For each of them, we give a bibliographic reference, that corresponds to the most recent article studying it and not the first one which introduced it.
We give the chosen tuning of the parameters, for parametric algorithms.
Algorithms that are not anytime use the exact value of the horizon $T$, and when increasing values of $T$ are studied for the same problem, of course they use the correct successive values.
We also give the name of the corresponding class in the \texttt{Policies} module in SMPyBandits.

@@

\begin{table}[!t]
\begin{footnotesize}  % WARNING
    \centering
    \begin{tabular}{c|*{5}{m{2cm}}} % WARNING size ?
    \textbf{Algorithms} $\;$ \textbackslash $\;$ $\mathbf{T=}$
        & $T_1 = 1000$ & $T_2 = 5000$ & $T_3 = 10000$ & $T_4 = 50000$ \\
        \hline
        $\varepsilon$-greedy &
            $R^{1}_{T_1,K_1} = 0 \pm 0$
                $R^{1}_{T_1,K_2} = 0 \pm 0$
                $R^{1}_{T_1,K_3} = 0 \pm 0$
                $R^{1}_{T_1,K_4} = 0 \pm 0$
                $R^{1}_{T_1,K_5} = 0 \pm 0$ &
            $R^{1}_{T_2,K_1} = 0 \pm 0$
                $R^{1}_{T_2,K_2} = 0 \pm 0$
                $R^{1}_{T_2,K_3} = 0 \pm 0$
                $R^{1}_{T_2,K_4} = 0 \pm 0$
                $R^{1}_{T_2,K_5} = 0 \pm 0$ &
            $R^{1}_{T_3,K_1} = 0 \pm 0$
                $R^{1}_{T_3,K_2} = 0 \pm 0$
                $R^{1}_{T_3,K_3} = 0 \pm 0$
                $R^{1}_{T_3,K_4} = 0 \pm 0$
                $R^{1}_{T_3,K_5} = 0 \pm 0$ &
            $R^{1}_{T_4,K_1} = 0 \pm 0$
                $R^{1}_{T_4,K_2} = 0 \pm 0$
                $R^{1}_{T_4,K_3} = 0 \pm 0$
                $R^{1}_{T_4,K_4} = 0 \pm 0$
                $R^{1}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Explore-then-Commit &
            $R^{2}_{T_1,K_1} = 0 \pm 0$
                $R^{2}_{T_1,K_2} = 0 \pm 0$
                $R^{2}_{T_1,K_3} = 0 \pm 0$
                $R^{2}_{T_1,K_4} = 0 \pm 0$
                $R^{2}_{T_1,K_5} = 0 \pm 0$ &
            $R^{2}_{T_2,K_1} = 0 \pm 0$
                $R^{2}_{T_2,K_2} = 0 \pm 0$
                $R^{2}_{T_2,K_3} = 0 \pm 0$
                $R^{2}_{T_2,K_4} = 0 \pm 0$
                $R^{2}_{T_2,K_5} = 0 \pm 0$ &
            $R^{2}_{T_3,K_1} = 0 \pm 0$
                $R^{2}_{T_3,K_2} = 0 \pm 0$
                $R^{2}_{T_3,K_3} = 0 \pm 0$
                $R^{2}_{T_3,K_4} = 0 \pm 0$
                $R^{2}_{T_3,K_5} = 0 \pm 0$ &
            $R^{2}_{T_4,K_1} = 0 \pm 0$
                $R^{2}_{T_4,K_2} = 0 \pm 0$
                $R^{2}_{T_4,K_3} = 0 \pm 0$
                $R^{2}_{T_4,K_4} = 0 \pm 0$
                $R^{2}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\mathrm{Exp}3^{++}$ &
            $R^3_{T_1,K_1} = 0 \pm 0$
                $R^3_{T_1,K_2} = 0 \pm 0$
                $R^3_{T_1,K_3} = 0 \pm 0$
                $R^3_{T_1,K_4} = 0 \pm 0$
                $R^3_{T_1,K_5} = 0 \pm 0$ &
            $R^3_{T_2,K_1} = 0 \pm 0$
                $R^3_{T_2,K_2} = 0 \pm 0$
                $R^3_{T_2,K_3} = 0 \pm 0$
                $R^3_{T_2,K_4} = 0 \pm 0$
                $R^3_{T_2,K_5} = 0 \pm 0$ &
            $R^3_{T_3,K_1} = 0 \pm 0$
                $R^3_{T_3,K_2} = 0 \pm 0$
                $R^3_{T_3,K_3} = 0 \pm 0$
                $R^3_{T_3,K_4} = 0 \pm 0$
                $R^3_{T_3,K_5} = 0 \pm 0$ &
            $R^3_{T_4,K_1} = 0 \pm 0$
                $R^3_{T_4,K_2} = 0 \pm 0$
                $R^3_{T_4,K_3} = 0 \pm 0$
                $R^3_{T_4,K_4} = 0 \pm 0$
                $R^3_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\UCB_1$ &
            $R^{4}_{T_1,K_1} = 0 \pm 0$
                $R^{4}_{T_1,K_2} = 0 \pm 0$
                $R^{4}_{T_1,K_3} = 0 \pm 0$
                $R^{4}_{T_1,K_4} = 0 \pm 0$
                $R^{4}_{T_1,K_5} = 0 \pm 0$ &
            $R^{4}_{T_2,K_1} = 0 \pm 0$
                $R^{4}_{T_2,K_2} = 0 \pm 0$
                $R^{4}_{T_2,K_3} = 0 \pm 0$
                $R^{4}_{T_2,K_4} = 0 \pm 0$
                $R^{4}_{T_2,K_5} = 0 \pm 0$ &
            $R^{4}_{T_3,K_1} = 0 \pm 0$
                $R^{4}_{T_3,K_2} = 0 \pm 0$
                $R^{4}_{T_3,K_3} = 0 \pm 0$
                $R^{4}_{T_3,K_4} = 0 \pm 0$
                $R^{4}_{T_3,K_5} = 0 \pm 0$ &
            $R^{4}_{T_4,K_1} = 0 \pm 0$
                $R^{4}_{T_4,K_2} = 0 \pm 0$
                $R^{4}_{T_4,K_3} = 0 \pm 0$
                $R^{4}_{T_4,K_4} = 0 \pm 0$
                $R^{4}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        \klUCB{} &
            $R^{5}_{T_1,K_1} = 0 \pm 0$
                $R^{5}_{T_1,K_2} = 0 \pm 0$
                $R^{5}_{T_1,K_3} = 0 \pm 0$
                $R^{5}_{T_1,K_4} = 0 \pm 0$
                $R^{5}_{T_1,K_5} = 0 \pm 0$ &
            $R^{5}_{T_2,K_1} = 0 \pm 0$
                $R^{5}_{T_2,K_2} = 0 \pm 0$
                $R^{5}_{T_2,K_3} = 0 \pm 0$
                $R^{5}_{T_2,K_4} = 0 \pm 0$
                $R^{5}_{T_2,K_5} = 0 \pm 0$ &
            $R^{5}_{T_3,K_1} = 0 \pm 0$
                $R^{5}_{T_3,K_2} = 0 \pm 0$
                $R^{5}_{T_3,K_3} = 0 \pm 0$
                $R^{5}_{T_3,K_4} = 0 \pm 0$
                $R^{5}_{T_3,K_5} = 0 \pm 0$ &
            $R^{5}_{T_4,K_1} = 0 \pm 0$
                $R^{5}_{T_4,K_2} = 0 \pm 0$
                $R^{5}_{T_4,K_3} = 0 \pm 0$
                $R^{5}_{T_4,K_4} = 0 \pm 0$
                $R^{5}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Thompson sampling &
            $R^{6}_{T_1,K_1} = 0 \pm 0$
                $R^{6}_{T_1,K_2} = 0 \pm 0$
                $R^{6}_{T_1,K_3} = 0 \pm 0$
                $R^{6}_{T_1,K_4} = 0 \pm 0$
                $R^{6}_{T_1,K_5} = 0 \pm 0$ &
            $R^{6}_{T_2,K_1} = 0 \pm 0$
                $R^{6}_{T_2,K_2} = 0 \pm 0$
                $R^{6}_{T_2,K_3} = 0 \pm 0$
                $R^{6}_{T_2,K_4} = 0 \pm 0$
                $R^{6}_{T_2,K_5} = 0 \pm 0$ &
            $R^{6}_{T_3,K_1} = 0 \pm 0$
                $R^{6}_{T_3,K_2} = 0 \pm 0$
                $R^{6}_{T_3,K_3} = 0 \pm 0$
                $R^{6}_{T_3,K_4} = 0 \pm 0$
                $R^{6}_{T_3,K_5} = 0 \pm 0$ &
            $R^{6}_{T_4,K_1} = 0 \pm 0$
                $R^{6}_{T_4,K_2} = 0 \pm 0$
                $R^{6}_{T_4,K_3} = 0 \pm 0$
                $R^{6}_{T_4,K_4} = 0 \pm 0$
                $R^{6}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Thompson sampling &
            $R^{7}_{T_1,K_1} = 0 \pm 0$
                $R^{7}_{T_1,K_2} = 0 \pm 0$
                $R^{7}_{T_1,K_3} = 0 \pm 0$
                $R^{7}_{T_1,K_4} = 0 \pm 0$
                $R^{7}_{T_1,K_5} = 0 \pm 0$ &
            $R^{7}_{T_2,K_1} = 0 \pm 0$
                $R^{7}_{T_2,K_2} = 0 \pm 0$
                $R^{7}_{T_2,K_3} = 0 \pm 0$
                $R^{7}_{T_2,K_4} = 0 \pm 0$
                $R^{7}_{T_2,K_5} = 0 \pm 0$ &
            $R^{7}_{T_3,K_1} = 0 \pm 0$
                $R^{7}_{T_3,K_2} = 0 \pm 0$
                $R^{7}_{T_3,K_3} = 0 \pm 0$
                $R^{7}_{T_3,K_4} = 0 \pm 0$
                $R^{7}_{T_3,K_5} = 0 \pm 0$ &
            $R^{7}_{T_4,K_1} = 0 \pm 0$
                $R^{7}_{T_4,K_2} = 0 \pm 0$
                $R^{7}_{T_4,K_3} = 0 \pm 0$
                $R^{7}_{T_4,K_4} = 0 \pm 0$
                $R^{7}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        AdBandits &
            $R^{8}_{T_1,K_1} = 0 \pm 0$
                $R^{8}_{T_1,K_2} = 0 \pm 0$
                $R^{8}_{T_1,K_3} = 0 \pm 0$
                $R^{8}_{T_1,K_4} = 0 \pm 0$
                $R^{8}_{T_1,K_5} = 0 \pm 0$ &
            $R^{8}_{T_2,K_1} = 0 \pm 0$
                $R^{8}_{T_2,K_2} = 0 \pm 0$
                $R^{8}_{T_2,K_3} = 0 \pm 0$
                $R^{8}_{T_2,K_4} = 0 \pm 0$
                $R^{8}_{T_2,K_5} = 0 \pm 0$ &
            $R^{8}_{T_3,K_1} = 0 \pm 0$
                $R^{8}_{T_3,K_2} = 0 \pm 0$
                $R^{8}_{T_3,K_3} = 0 \pm 0$
                $R^{8}_{T_3,K_4} = 0 \pm 0$
                $R^{8}_{T_3,K_5} = 0 \pm 0$ &
            $R^{8}_{T_4,K_1} = 0 \pm 0$
                $R^{8}_{T_4,K_2} = 0 \pm 0$
                $R^{8}_{T_4,K_3} = 0 \pm 0$
                $R^{8}_{T_4,K_4} = 0 \pm 0$
                $R^{8}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        BESA &
            $R^{9}_{T_1,K_1} = 0 \pm 0$
                $R^{9}_{T_1,K_2} = 0 \pm 0$
                $R^{9}_{T_1,K_3} = 0 \pm 0$
                $R^{9}_{T_1,K_4} = 0 \pm 0$
                $R^{9}_{T_1,K_5} = 0 \pm 0$ &
            $R^{9}_{T_2,K_1} = 0 \pm 0$
                $R^{9}_{T_2,K_2} = 0 \pm 0$
                $R^{9}_{T_2,K_3} = 0 \pm 0$
                $R^{9}_{T_2,K_4} = 0 \pm 0$
                $R^{9}_{T_2,K_5} = 0 \pm 0$ &
            $R^{9}_{T_3,K_1} = 0 \pm 0$
                $R^{9}_{T_3,K_2} = 0 \pm 0$
                $R^{9}_{T_3,K_3} = 0 \pm 0$
                $R^{9}_{T_3,K_4} = 0 \pm 0$
                $R^{9}_{T_3,K_5} = 0 \pm 0$ &
            $R^{9}_{T_4,K_1} = 0 \pm 0$
                $R^{9}_{T_4,K_2} = 0 \pm 0$
                $R^{9}_{T_4,K_3} = 0 \pm 0$
                $R^{9}_{T_4,K_4} = 0 \pm 0$
                $R^{9}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for $9$ different algorithms on \textbf{problem 1} with different values of time $T$ and number of arm $K$.
    }
    \label{table:3:meanRegret_problem1}
\end{footnotesize}  % WARNING
\end{table}

\begin{table}[!t]
\begin{footnotesize}  % WARNING
    \centering
    \begin{tabular}{c|*{5}{m{2cm}}} % WARNING size ?
    \textbf{Algorithms} $\;$ \textbackslash $\;$ $\mathbf{T=}$
        & $T_1 = 1000$ & $T_2 = 5000$ & $T_3 = 10000$ & $T_4 = 50000$ \\
        \hline
        $\varepsilon$-greedy &
            $R^{'1}_{T_1,K_1} = 0 \pm 0$
                $R^{'1}_{T_1,K_2} = 0 \pm 0$
                $R^{'1}_{T_1,K_3} = 0 \pm 0$
                $R^{'1}_{T_1,K_4} = 0 \pm 0$
                $R^{'1}_{T_1,K_5} = 0 \pm 0$ &
            $R^{'1}_{T_2,K_1} = 0 \pm 0$
                $R^{'1}_{T_2,K_2} = 0 \pm 0$
                $R^{'1}_{T_2,K_3} = 0 \pm 0$
                $R^{'1}_{T_2,K_4} = 0 \pm 0$
                $R^{'1}_{T_2,K_5} = 0 \pm 0$ &
            $R^{'1}_{T_3,K_1} = 0 \pm 0$
                $R^{'1}_{T_3,K_2} = 0 \pm 0$
                $R^{'1}_{T_3,K_3} = 0 \pm 0$
                $R^{'1}_{T_3,K_4} = 0 \pm 0$
                $R^{'1}_{T_3,K_5} = 0 \pm 0$ &
            $R^{'1}_{T_4,K_1} = 0 \pm 0$
                $R^{'1}_{T_4,K_2} = 0 \pm 0$
                $R^{'1}_{T_4,K_3} = 0 \pm 0$
                $R^{'1}_{T_4,K_4} = 0 \pm 0$
                $R^{'1}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Explore-then-Commit &
            $R^{'2}_{T_1,K_1} = 0 \pm 0$
                $R^{'2}_{T_1,K_2} = 0 \pm 0$
                $R^{'2}_{T_1,K_3} = 0 \pm 0$
                $R^{'2}_{T_1,K_4} = 0 \pm 0$
                $R^{'2}_{T_1,K_5} = 0 \pm 0$ &
            $R^{'2}_{T_2,K_1} = 0 \pm 0$
                $R^{'2}_{T_2,K_2} = 0 \pm 0$
                $R^{'2}_{T_2,K_3} = 0 \pm 0$
                $R^{'2}_{T_2,K_4} = 0 \pm 0$
                $R^{'2}_{T_2,K_5} = 0 \pm 0$ &
            $R^{'2}_{T_3,K_1} = 0 \pm 0$
                $R^{'2}_{T_3,K_2} = 0 \pm 0$
                $R^{'2}_{T_3,K_3} = 0 \pm 0$
                $R^{'2}_{T_3,K_4} = 0 \pm 0$
                $R^{'2}_{T_3,K_5} = 0 \pm 0$ &
            $R^{'2}_{T_4,K_1} = 0 \pm 0$
                $R^{'2}_{T_4,K_2} = 0 \pm 0$
                $R^{'2}_{T_4,K_3} = 0 \pm 0$
                $R^{'2}_{T_4,K_4} = 0 \pm 0$
                $R^{'2}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\mathrm{Exp}3^{++}$ &
            $R^{'3}_{T_1,K_1} = 0 \pm 0$
                $R^{'3}_{T_1,K_2} = 0 \pm 0$
                $R^{'3}_{T_1,K_3} = 0 \pm 0$
                $R^{'3}_{T_1,K_4} = 0 \pm 0$
                $R^{'3}_{T_1,K_5} = 0 \pm 0$ &
            $R^{'3}_{T_2,K_1} = 0 \pm 0$
                $R^{'3}_{T_2,K_2} = 0 \pm 0$
                $R^{'3}_{T_2,K_3} = 0 \pm 0$
                $R^{'3}_{T_2,K_4} = 0 \pm 0$
                $R^{'3}_{T_2,K_5} = 0 \pm 0$ &
            $R^{'3}_{T_3,K_1} = 0 \pm 0$
                $R^{'3}_{T_3,K_2} = 0 \pm 0$
                $R^{'3}_{T_3,K_3} = 0 \pm 0$
                $R^{'3}_{T_3,K_4} = 0 \pm 0$

>>>>

We consider the nine following algorithms, and seven more are described in Appendix~\ref{sub:3:additionalExperiments}.
For each of them, we give a bibliographic reference, that corresponds to the most recent article studying it and not the first one which introduced it.
We give the chosen tuning of the parameters, for parametric algorithms.
Algorithms that are not anytime use the exact value of the horizon $T$, and when increasing values of $T$ are studied for the same problem, of course they use the correct successive values. \\
%
\indent
For reproducibility, we also give in ``\texttt{typewriter font}'' the name of the corresponding class in the \texttt{Policies} module in SMPyBandits.

@@

% \begin{table}[!t]
% \begin{footnotesize}  % WARNING
%     \centering
%     \begin{tabular}{c|*{5}{m{2cm}}} % WARNING size ?
%     \textbf{Algorithms} $\;$ \textbackslash $\;$ $\mathbf{T=}$
%         & $T_1 = 1000$ & $T_2 = 5000$ & $T_3 = 10000$ & $T_4 = 50000$ \\
%         \hline
%         $\varepsilon$-greedy &
%             $R^{1}_{T_1,K_1} = 0 \pm 0$
%                 $R^{1}_{T_1,K_2} = 0 \pm 0$
%                 $R^{1}_{T_1,K_3} = 0 \pm 0$
%                 $R^{1}_{T_1,K_4} = 0 \pm 0$
%                 $R^{1}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{1}_{T_2,K_1} = 0 \pm 0$
%                 $R^{1}_{T_2,K_2} = 0 \pm 0$
%                 $R^{1}_{T_2,K_3} = 0 \pm 0$
%                 $R^{1}_{T_2,K_4} = 0 \pm 0$
%                 $R^{1}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{1}_{T_3,K_1} = 0 \pm 0$
%                 $R^{1}_{T_3,K_2} = 0 \pm 0$
%                 $R^{1}_{T_3,K_3} = 0 \pm 0$
%                 $R^{1}_{T_3,K_4} = 0 \pm 0$
%                 $R^{1}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{1}_{T_4,K_1} = 0 \pm 0$
%                 $R^{1}_{T_4,K_2} = 0 \pm 0$
%                 $R^{1}_{T_4,K_3} = 0 \pm 0$
%                 $R^{1}_{T_4,K_4} = 0 \pm 0$
%                 $R^{1}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         Explore-then-Commit &
%             $R^{2}_{T_1,K_1} = 0 \pm 0$
%                 $R^{2}_{T_1,K_2} = 0 \pm 0$
%                 $R^{2}_{T_1,K_3} = 0 \pm 0$
%                 $R^{2}_{T_1,K_4} = 0 \pm 0$
%                 $R^{2}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{2}_{T_2,K_1} = 0 \pm 0$
%                 $R^{2}_{T_2,K_2} = 0 \pm 0$
%                 $R^{2}_{T_2,K_3} = 0 \pm 0$
%                 $R^{2}_{T_2,K_4} = 0 \pm 0$
%                 $R^{2}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{2}_{T_3,K_1} = 0 \pm 0$
%                 $R^{2}_{T_3,K_2} = 0 \pm 0$
%                 $R^{2}_{T_3,K_3} = 0 \pm 0$
%                 $R^{2}_{T_3,K_4} = 0 \pm 0$
%                 $R^{2}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{2}_{T_4,K_1} = 0 \pm 0$
%                 $R^{2}_{T_4,K_2} = 0 \pm 0$
%                 $R^{2}_{T_4,K_3} = 0 \pm 0$
%                 $R^{2}_{T_4,K_4} = 0 \pm 0$
%                 $R^{2}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         $\mathrm{Exp}3^{++}$ &
%             $R^3_{T_1,K_1} = 0 \pm 0$
%                 $R^3_{T_1,K_2} = 0 \pm 0$
%                 $R^3_{T_1,K_3} = 0 \pm 0$
%                 $R^3_{T_1,K_4} = 0 \pm 0$
%                 $R^3_{T_1,K_5} = 0 \pm 0$ &
%             $R^3_{T_2,K_1} = 0 \pm 0$
%                 $R^3_{T_2,K_2} = 0 \pm 0$
%                 $R^3_{T_2,K_3} = 0 \pm 0$
%                 $R^3_{T_2,K_4} = 0 \pm 0$
%                 $R^3_{T_2,K_5} = 0 \pm 0$ &
%             $R^3_{T_3,K_1} = 0 \pm 0$
%                 $R^3_{T_3,K_2} = 0 \pm 0$
%                 $R^3_{T_3,K_3} = 0 \pm 0$
%                 $R^3_{T_3,K_4} = 0 \pm 0$
%                 $R^3_{T_3,K_5} = 0 \pm 0$ &
%             $R^3_{T_4,K_1} = 0 \pm 0$
%                 $R^3_{T_4,K_2} = 0 \pm 0$
%                 $R^3_{T_4,K_3} = 0 \pm 0$
%                 $R^3_{T_4,K_4} = 0 \pm 0$
%                 $R^3_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         $\UCB_1$ &
%             $R^{4}_{T_1,K_1} = 0 \pm 0$
%                 $R^{4}_{T_1,K_2} = 0 \pm 0$
%                 $R^{4}_{T_1,K_3} = 0 \pm 0$
%                 $R^{4}_{T_1,K_4} = 0 \pm 0$
%                 $R^{4}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{4}_{T_2,K_1} = 0 \pm 0$
%                 $R^{4}_{T_2,K_2} = 0 \pm 0$
%                 $R^{4}_{T_2,K_3} = 0 \pm 0$
%                 $R^{4}_{T_2,K_4} = 0 \pm 0$
%                 $R^{4}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{4}_{T_3,K_1} = 0 \pm 0$
%                 $R^{4}_{T_3,K_2} = 0 \pm 0$
%                 $R^{4}_{T_3,K_3} = 0 \pm 0$
%                 $R^{4}_{T_3,K_4} = 0 \pm 0$
%                 $R^{4}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{4}_{T_4,K_1} = 0 \pm 0$
%                 $R^{4}_{T_4,K_2} = 0 \pm 0$
%                 $R^{4}_{T_4,K_3} = 0 \pm 0$
%                 $R^{4}_{T_4,K_4} = 0 \pm 0$
%                 $R^{4}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         \klUCB{} &
%             $R^{5}_{T_1,K_1} = 0 \pm 0$
%                 $R^{5}_{T_1,K_2} = 0 \pm 0$
%                 $R^{5}_{T_1,K_3} = 0 \pm 0$
%                 $R^{5}_{T_1,K_4} = 0 \pm 0$
%                 $R^{5}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{5}_{T_2,K_1} = 0 \pm 0$
%                 $R^{5}_{T_2,K_2} = 0 \pm 0$
%                 $R^{5}_{T_2,K_3} = 0 \pm 0$
%                 $R^{5}_{T_2,K_4} = 0 \pm 0$
%                 $R^{5}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{5}_{T_3,K_1} = 0 \pm 0$
%                 $R^{5}_{T_3,K_2} = 0 \pm 0$
%                 $R^{5}_{T_3,K_3} = 0 \pm 0$
%                 $R^{5}_{T_3,K_4} = 0 \pm 0$
%                 $R^{5}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{5}_{T_4,K_1} = 0 \pm 0$
%                 $R^{5}_{T_4,K_2} = 0 \pm 0$
%                 $R^{5}_{T_4,K_3} = 0 \pm 0$
%                 $R^{5}_{T_4,K_4} = 0 \pm 0$
%                 $R^{5}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         Thompson sampling &
%             $R^{6}_{T_1,K_1} = 0 \pm 0$
%                 $R^{6}_{T_1,K_2} = 0 \pm 0$
%                 $R^{6}_{T_1,K_3} = 0 \pm 0$
%                 $R^{6}_{T_1,K_4} = 0 \pm 0$
%                 $R^{6}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{6}_{T_2,K_1} = 0 \pm 0$
%                 $R^{6}_{T_2,K_2} = 0 \pm 0$
%                 $R^{6}_{T_2,K_3} = 0 \pm 0$
%                 $R^{6}_{T_2,K_4} = 0 \pm 0$
%                 $R^{6}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{6}_{T_3,K_1} = 0 \pm 0$
%                 $R^{6}_{T_3,K_2} = 0 \pm 0$
%                 $R^{6}_{T_3,K_3} = 0 \pm 0$
%                 $R^{6}_{T_3,K_4} = 0 \pm 0$
%                 $R^{6}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{6}_{T_4,K_1} = 0 \pm 0$
%                 $R^{6}_{T_4,K_2} = 0 \pm 0$
%                 $R^{6}_{T_4,K_3} = 0 \pm 0$
%                 $R^{6}_{T_4,K_4} = 0 \pm 0$
%                 $R^{6}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         Thompson sampling &
%             $R^{7}_{T_1,K_1} = 0 \pm 0$
%                 $R^{7}_{T_1,K_2} = 0 \pm 0$
%                 $R^{7}_{T_1,K_3} = 0 \pm 0$
%                 $R^{7}_{T_1,K_4} = 0 \pm 0$
%                 $R^{7}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{7}_{T_2,K_1} = 0 \pm 0$
%                 $R^{7}_{T_2,K_2} = 0 \pm 0$
%                 $R^{7}_{T_2,K_3} = 0 \pm 0$
%                 $R^{7}_{T_2,K_4} = 0 \pm 0$
%                 $R^{7}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{7}_{T_3,K_1} = 0 \pm 0$
%                 $R^{7}_{T_3,K_2} = 0 \pm 0$
%                 $R^{7}_{T_3,K_3} = 0 \pm 0$
%                 $R^{7}_{T_3,K_4} = 0 \pm 0$
%                 $R^{7}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{7}_{T_4,K_1} = 0 \pm 0$
%                 $R^{7}_{T_4,K_2} = 0 \pm 0$
%                 $R^{7}_{T_4,K_3} = 0 \pm 0$
%                 $R^{7}_{T_4,K_4} = 0 \pm 0$
%                 $R^{7}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         AdBandits &
%             $R^{8}_{T_1,K_1} = 0 \pm 0$
%                 $R^{8}_{T_1,K_2} = 0 \pm 0$
%                 $R^{8}_{T_1,K_3} = 0 \pm 0$
%                 $R^{8}_{T_1,K_4} = 0 \pm 0$
%                 $R^{8}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{8}_{T_2,K_1} = 0 \pm 0$
%                 $R^{8}_{T_2,K_2} = 0 \pm 0$
%                 $R^{8}_{T_2,K_3} = 0 \pm 0$
%                 $R^{8}_{T_2,K_4} = 0 \pm 0$
%                 $R^{8}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{8}_{T_3,K_1} = 0 \pm 0$
%                 $R^{8}_{T_3,K_2} = 0 \pm 0$
%                 $R^{8}_{T_3,K_3} = 0 \pm 0$
%                 $R^{8}_{T_3,K_4} = 0 \pm 0$
%                 $R^{8}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{8}_{T_4,K_1} = 0 \pm 0$
%                 $R^{8}_{T_4,K_2} = 0 \pm 0$
%                 $R^{8}_{T_4,K_3} = 0 \pm 0$
%                 $R^{8}_{T_4,K_4} = 0 \pm 0$
%                 $R^{8}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         BESA &
%             $R^{9}_{T_1,K_1} = 0 \pm 0$
%                 $R^{9}_{T_1,K_2} = 0 \pm 0$
%                 $R^{9}_{T_1,K_3} = 0 \pm 0$
%                 $R^{9}_{T_1,K_4} = 0 \pm 0$
%                 $R^{9}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{9}_{T_2,K_1} = 0 \pm 0$
%                 $R^{9}_{T_2,K_2} = 0 \pm 0$
%                 $R^{9}_{T_2,K_3} = 0 \pm 0$
%                 $R^{9}_{T_2,K_4} = 0 \pm 0$
%                 $R^{9}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{9}_{T_3,K_1} = 0 \pm 0$
%                 $R^{9}_{T_3,K_2} = 0 \pm 0$
%                 $R^{9}_{T_3,K_3} = 0 \pm 0$
%                 $R^{9}_{T_3,K_4} = 0 \pm 0$
%                 $R^{9}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{9}_{T_4,K_1} = 0 \pm 0$
%                 $R^{9}_{T_4,K_2} = 0 \pm 0$
%                 $R^{9}_{T_4,K_3} = 0 \pm 0$
%                 $R^{9}_{T_4,K_4} = 0 \pm 0$
%                 $R^{9}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%     \end{tabular}
%     \caption{Mean regret $\pm$ $1$ std-dev, for $9$ different algorithms on \textbf{problem 1} with different values of time $T$ and number of arm $K$.
%     }
%     \label{table:3:meanRegret_problem1}
% \end{footnotesize}  % WARNING
% \end{table}

% \begin{table}[!t]
% \begin{footnotesize}  % WARNING
%     \centering
%     \begin{tabular}{c|*{5}{m{2cm}}} % WARNING size ?
%     \textbf{Algorithms} $\;$ \textbackslash $\;$ $\mathbf{T=}$
%         & $T_1 = 1000$ & $T_2 = 5000$ & $T_3 = 10000$ & $T_4 = 50000$ \\
%         \hline
%         $\varepsilon$-greedy &
%             $R^{'1}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'1}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'1}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'1}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_5} = 0 \pm 0$ \\
%         \hline
%         Explore-then-Commit &
%             $R^{'2}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'2}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'2}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'2}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_4} = 0 \pm 0$
